### 2021-04-07 pldi21/implementation.tex
second round

Uniquely, every editor state in Hazel is 
semantically meaningful: it has a type, it can be evaluated, and it can be transformed 
in a type-aware manner. This implies that livelits remain fully functional at all times, 
even when the program is incomplete or erroneous. Hazel achieves this ``gap-free'' liveness guarantee by automatically inserting explicit holes as necessary 
while the user edits 
the program. Formally, Hazel is a type-aware structure editor \cite{Hazelnut}, rather than a text editor, 
although the developers are aiming to maintain a text-like experience (this effort is orthogonal to our own).

>>>>

Uniquely, every editor state in Hazel is 
semantically meaningful: it has a type, it can be evaluated, and it can be transformed 
in a type-aware manner. This implies that livelits remain fully functional at all times, 
even when the program is incomplete or erroneous. Hazel achieves this ``gap-free'' liveness guarantee by automatically inserting explicit holes as necessary 
while the user edits 
the program. Formally, Hazel is a type-aware structure editor \cite{Hazelnut}, rather than a text editor, 
although the developers are aiming to maintain a text-like experience (this effort is orthogonal to our own). 
To maintain this guarantee, Hazel inserts empty holes where there are missing terms, 
and non-empty holes as markers of errors. To maintain this invariant in the presence of livelits, 
new non-empty holes are needed to mark each of the failure modes suggested by the premises of the \rulename{ELivelit} rule in Fig.~\ref{fig:expansion}. 
In particular, non-empty holes mark (1) the invocation of an unbound livelit; (2) the invocation of a livelit 
with a model value of the wrong type; 
(3) a run-time error during evaluation of \li{init}, \li{update}, or \li{expand} functions (which manifests as a run-time hole); (4) 
expansion validation failure (i.e. that the parameterized expansion is of the wrong type given the splice list).  
Errors in view generation are not considered semantic errors (they display as error messages where the livelit GUI would have appeared.)
